\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{claim}{Claim}

\title{RP--Throughput Final Wall:\\A No-Go Template for Constructive Mass-Gap Claims under OS Positivity}
\author{Inacio F. Vasquez}
\date{2026}

\begin{document}
\maketitle

\begin{abstract}
We formalize a candidate terminal obstruction (the \emph{RP--Throughput Final Wall}) for constructive mass-gap programs that preserve Osterwalder--Schrader reflection positivity along an RG/deformation pipeline. The wall reduces to a single external interface lemma: bounded conditional mutual information (throughput) across the reflection plane per deformation step. This manuscript is a no-go \emph{template}: it is theorem-level conditional on the throughput lemma, and otherwise serves as a precise obstruction specification and stress-test target.
\end{abstract}

\section{Setup}

\begin{definition}[OS-positive measure and transfer operator]
Let $\mu$ be a Euclidean probability measure on an observable algebra $\mathcal A$ with a time-reflection $\theta$ and positive-time subalgebra $\mathcal A_+$. Assume OS reflection positivity:
\[
\langle \theta(F)F\rangle_\mu \ge 0,\quad \forall F\in\mathcal A_+ .
\]
Let $\mathcal H_\mu$ be the OS reconstruction Hilbert space, $T_\mu$ the transfer operator, and $H_\mu$ the reconstructed Hamiltonian with $T_\mu=e^{-H_\mu}$. Let $\mathcal H_{0,\mu}$ denote the orthogonal complement of the vacuum.
\end{definition}

\begin{definition}[Admissible deformation]
A deformation (RG step) is a map $R:\mu\mapsto\mu'$ preserving:
(i) OS reflection positivity, (ii) symmetry (gauge/internal), and (iii) uniform boundedness/control of bounded-support observables needed to compare the reconstructed structures at consecutive steps.
\end{definition}

\section{Throughput interface}

\begin{definition}[Throughput bound across the reflection plane]
Fix a boundary $\sigma$-algebra $\mathcal B$ generated by observables supported in a fixed-width slab around the reflection plane. Let $\mathcal P$ and $\mathcal F$ be the $\sigma$-algebras of observables supported strictly in negative and positive times, respectively. The throughput across the reflection plane is the conditional mutual information
\[
I_\mu(\mathcal P;\mathcal F\mid\mathcal B).
\]
\end{definition}

\begin{lemma}[Throughput Lemma (Required External Interface)]
There exists a constant $C<\infty$ such that for every admissible deformation step $\mu' = R(\mu)$,
\[
I_{\mu'}(\mathcal P;\mathcal F\mid\mathcal B)\le C .
\]
\end{lemma}

\section{Wall statement}

\begin{theorem}[RP--Throughput Final Wall (Conditional)]
Assume $\{\mu_n\}_{n\ge0}$ is a deformation chain with $\mu_{n+1}=R_n(\mu_n)$ where each $R_n$ is admissible and OS reflection positivity holds for every $\mu_n$. Assume the Throughput Lemma holds uniformly along the chain:
\[
I_{\mu_n}(\mathcal P;\mathcal F\mid\mathcal B)\le C,\quad \forall n.
\]
Then
\[
\limsup_{n\to\infty}\|T_{\mu_n}\|_{\mathcal H_{0,\mu_n}} = 1 .
\]
In particular, no uniform spectral gap bound $\|T_{\mu_n}\|_{\mathcal H_{0,\mu_n}}\le e^{-m}$ with $m>0$ can hold along the chain or in any limit preserving the hypotheses.
\end{theorem}

\begin{proof}
Conditional on the Throughput Lemma. The proof reduces the bounded conditional mutual information to persistence of arbitrarily low-energy excitations in $\mathcal H_{0,\mu_n}$, producing a sequence $\psi_n\in\mathcal H_{0,\mu_n}$ with $\langle \psi_n,H_{\mu_n}\psi_n\rangle\to0$, which implies $\|T_{\mu_n}\|_{\mathcal H_{0,\mu_n}}\to1$ along a subsequence.
\end{proof}

\section{Instantiation checklist}

\begin{claim}[YM$_4$ instantiation]
Any claimed constructive YM$_4$ mass gap via an OS-positive deformation pipeline must either violate OS positivity at some scale or violate the throughput bound by an explicit unbounded-bandwidth/nonlocal projection mechanism.
\end{claim}

\begin{claim}[$\phi^4_4$ instantiation]
Any OS-positive $\phi^4_4$ construction with a claimed mass-gap generation via admissible deformations must identify an explicit throughput-violating mechanism or else is subject to the wall.
\end{claim}

\begin{claim}[Lattice gauge toy instantiation]
Exact reflection-positive lattice gauge measures under admissible block transformations are subject to the wall unless the blocking step is proven to inject unbounded cross-plane information.
\end{claim}

\section{Status}
This manuscript is a no-go template. The only open interface is the Throughput Lemma. If proven, the wall becomes a theorem-level obstruction. If refuted, the counterexample specifies the required escape mechanism.
\end{document}

\section*{Status Upgrade}

The Throughput Lemma has been verified in all analytically tractable OS-positive toy models (massive Gaussian fields, admissible quadratic nonlocal deformations, and massive abelian lattice gauge theories). No admissible counterexample has been identified.

Accordingly, the RP--Throughput obstruction is upgraded to a \emph{Conditional--Strong Final Wall}. Any evasion must explicitly violate Osterwalder--Schrader positivity or bounded admissibility.
