\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,geometry,hyperref}
\geometry{margin=1in}

\newtheorem{theorem}{Theorem}
\newtheorem{axiom}{Axiom}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{hypothesis}{Hypothesis}

\title{Importing Hilbert--Schmidt and Kato Obstructions into\\
Pulse and Operator--Flow Locality Collapse}
\author{Inacio F. Vasquez}
\date{2026}

\begin{document}
\maketitle

\begin{abstract}
This note imports certified Hilbert--Schmidt and Kato-type obstructions into
the Pulse and Operator--Flow Locality Collapse (OFLC) framework.
The imported results are established by computer-assisted verification
and are used solely as negative inputs constraining admissible locality-based
approaches to the Yang--Mills mass gap problem.
\end{abstract}

\section{Imported Computer-Assisted Results}

\begin{remark}[Certified HS/Kato Obstructions]
The following results are imported from the repository
\texttt{yang-mills-hs-gap-cert}:
\begin{itemize}
\item Stability of a Kato-type invariant under cutoff variation,
verified by the executable script
\texttt{verification/kato\_invariant\_test.py};
\item A two-bubble instability demonstrating the failure of uniform
Hilbert--Schmidt coercivity, verified by
\texttt{verification/kato\_two\_bubble\_test.py}.
\end{itemize}
These results are machine-checked, reproducible, and certify
limitations of Hilbert--Schmidt and Kato-based coercivity arguments.
\end{remark}

\section{Pulse and OFLC (Conditional)}

\begin{axiom}[Pulse — Conditional]
Assume there exist constants $C,c>0$ and a scale $\rho(\Lambda)$ such that
for all strictly local observables $A$ and all $0 \le n \le c\log\Lambda$,
\[
\|\mathrm{ad}_{H_\Lambda^{\mathrm{ren}}}^n(A)\|
\le C^n n!\,\rho(\Lambda)^n .
\]
\end{axiom}

\begin{definition}[Operator--Flow Locality Collapse]
Operator--Flow Locality Collapse (OFLC) refers to the regime in which
operator growth under Heisenberg evolution cannot be bounded by any
cutoff-uniform Lieb--Robinson velocity.
\end{definition}

\begin{theorem}[Conditional OFLC Constraint]
Assume the Pulse axiom holds with $\rho(\Lambda)\to\infty$ as
$\Lambda\to\infty$.  
Given the certified failure of Hilbert--Schmidt and Kato-type coercivity,
no locality-based argument relying on such coercivity can establish
a uniform mass gap in the continuum limit.
\end{theorem}

\section{Scope and Status}

All statements in this note are conditional.
Computer-assisted verification is used exclusively to certify
analytic obstructions, not to establish the Yang--Mills mass gap.
Any positive resolution must therefore invoke nonlocal or
non-coercive mechanisms beyond the excluded classes.

\end{document}
